Paper 2: Vitamin D

### 2018-03-16 doc/vitaminD.Rmd
made plots more visible for seminar presentation
modified GEE model to remove season and include BMI

knitr::opts_chunk$set(collapse = TRUE, echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
devtools::load_all()
load_data(update = TRUE)
set_options()
# extrafont::loadfonts(device="win")
```

@@

# value
vitd %>%
  dplyr::group_by(vitdStatus) %>% 
  dplyr::summarise(Median = median(log(udbpCr)), 
                   IQR = IQR(log(udbpCr))
                   )

@@

dsBase %>% 
  scatter_plot_slides("log(VitaminD)", "log(udbpCr)", 
               "log serum 25(OH)D",
               "log uVDBP:cr (μg/mmol)")

@@

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCrBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", 
                       "Ethnicity", "MET", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

tab_nums(gee_vitd_baseline, "GEE results for uVDBP at baseline (predictor) with 25(OH)D and (outcomes), adjusted for follow-up duration (in months), baseline age, sex, ethnicity, physical activity (MET), BMI, diabetes status, and seasonality; subjects with deficient vitamin D status at baseline excluded (n = 713).")

@@

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCr",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

>>>>

knitr::opts_chunk$set(collapse = TRUE, echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
devtools::load_all()
# load_data(update = TRUE)
set_options()
# extrafont::loadfonts(device="win")
```

@@

# value
vitd %>%
  dplyr::group_by(vitdStatus) %>% 
  dplyr::summarise(n = n(),
                   Median = median(log(udbpCr)), 
                   lower = quantile(log(udbpCr), probs = 0.25),
                   higher = quantile(log(udbpCr), probs = 0.75),
                   IQR = IQR(log(udbpCr))
                   )

@@

dsBase %>% 
  scatter_plot_slides("log(VitaminD)", "log(udbpCr)", 
               "log serum 25(OH)D (nmol/L)",
               "log uVDBP:cr (μg/mmol)")

@@

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCrBase",
            covars = c("YearsFromBaseline", "ageBase", "Sex", 
                       "Ethnicity", "BMI", "MET", "dmStatus", "Season")) %>% 
            # intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

@@

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCr",
            covars = c("YearsFromBaseline", "ageBase", "Sex", "Ethnicity", "BMI",
                       "MET", "dmStatus", "Season")) %>% 
            # intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)
